Pollution, agricultural productivity, and development: Evidence from coal in plants in India\footnote{All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}

### 2023-04-07 draft/draft.tex
changes to draft, analyses, and cleaning

\title{Blowing in the wind: Pollution and agricultural productivity in India\footnote{I thank Marc Bellemare and David Sungho Park for comments and suggestions that greatly improved the quality of the paper. The usual disclaimer applies. All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}}
\author{Joshua D. Merfeld\footnote{KDI School of Public Policy and Management and IZA; \href{mailto:merfeld@kdis.ac.kr}{\nolinkurl{merfeld@kdis.ac.kr}}}}
\date{2023-03-02}

@@

@@

\caption{\label{tab:plantresultstable}Local characteristics and the construction of coal plants}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{1991 census} & \multicolumn{2}{c}{2001 census} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
  & 1991 & 2001 & 2001 & 2011\\
\midrule
pop (log) & 0.010*** & 0.001*** & 0.017*** & 0.004***\\
 & (0.000) & (0.000) & (0.000) & (0.000)\\
area (log) & -0.006*** & 0.001** & -0.015*** & -0.001***\\
 & (0.001) & (0.000) & (0.000) & (0.000)\\
literacy (prop) & 0.024*** & 0.017*** & 0.032*** & 0.029***\\
 & (0.003) & (0.002) & (0.002) & (0.002)\\
ag productivity &  &  & 0.026*** & 0.004***\\
 &  &  & (0.001) & (0.000)\\
sub-sample & all & no plant & all & no plant\\
\midrule
observations & 283,021 & 264,265 & 508,784 & 469,004\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Robust standard errors are in parentheses. The outcome in the first column is whether the village is within 30km of a coal plant in 1991. The second column is whether a village in 1991 will have a coal plant in 2001, conditional on not having one in 1991. The last two columns are similarly defined, except using 2001 and 2011 as the years. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtable}Wind direction and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}}
\toprule
  & (1) & (2) & (3)\\
\midrule
wind days & -0.0078*** & -0.0069*** & -0.0062***\\
 & (0.0007) & (0.0007) & (0.0006)\\
rain (z) &  & 0.0854*** & -0.0424***\\
 &  & (0.0018) & (0.0046)\\
mean temp (10s) &  & -0.0021*** & 0.1321***\\
 &  & (0.0001) & (0.0034)\\
rain square &  &  & -0.0010***\\
 &  &  & (0.0001)\\
temp square &  &  & -0.0002***\\
 &  &  & \vphantom{1} (0.0000)\\
rain times temp &  &  & 0.0003***\\
 &  &  & (0.0000)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{}\\
village & Yes & Yes & Yes\\
year & Yes & Yes & Yes\\
\midrule
observations & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablepm}Particulate matter (PM 2.5) and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}}
\toprule
  & (1) & (2) & (3)\\
\midrule
particulate matter & -0.042*** & -0.044*** & -0.032***\\
(log PM 2.5) & (0.003) & (0.003) & (0.003)\\
weather & No & Yes & Yes\\
weather (expanded) & No & No & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{}\\
village & Yes & Yes & Yes\\
year & Yes & Yes & Yes\\
\midrule
observations & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtabletwo}Pollution and agricultural productivity, IV estimates}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3)\\
\midrule
particulate matter & -0.941*** & -0.813*** & -0.728***\\
(log PM 2.5) & (0.078) & (0.076) & (0.075)\\
weather & No & Yes & Yes\\
weather (expanded) & No & No & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{}\\
village & Yes & Yes & Yes\\
year & Yes & Yes & Yes\\
\midrule
F (first stage) & 1,235 & 1,262 & 1,263\\
observations & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablehet}Heterogeneity in the effects of pollution on productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{wind} & \multicolumn{2}{c}{yield} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
  & >p(50) & <=p(50) & >p(50) & <=p(50) & \\
\midrule
PM 2.5 & -0.767*** & -0.328*** & -1.130*** & -0.690*** & -0.409**\\
 & (0.104) & (0.095) & (0.060) & (0.146) & (0.160)\\
PM times rain &  &  &  &  & 0.061***\\
 &  &  &  &  & (0.014)\\
weather & Yes & Yes & Yes & Yes & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village & Yes & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes & Yes\\
\midrule
F (1st stage, PM) & 684 & 491 & 688 & 484 & 865\\
F (1st stage, PM times rain) &  &  &  &  & 1,437\\
observations & 617,804 & 649,118 & 634,342 & 632,580 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. The first two columns split the sample based on the median exposure (by village). The second two columns split the sample based on initial -- the first year available -- agricultural productivity. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:labortable}Wind direction and labor allocation by rural status}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}}
\toprule
  & all & all & self & wage & farm & non-farm\\
\midrule
\textbf{panel a: all} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
wind & -0.011 & -0.009 & 0.030 & -0.049 & -0.009 & -0.010\\
 & (0.031) & (0.034) & (0.039) & (0.034) & (0.034) & (0.033)\\
DV mean & 3.303 & 3.303 & 1.862 & 1.442 & 0.789 & 2.514\\
observations & 523,075 & 522,957 & 522,957 & 522,957 & 522,957 & 522,957\\
\midrule
\textbf{panel b: rural} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
wind & -0.006 & -0.034 & 0.068 & -0.102*** & -0.024 & -0.010\\
 & (0.044) & (0.040) & (0.043) & (0.035) & (0.043) & (0.036)\\
DV mean & 3.494 & 3.494 & 2.184 & 1.311 & 1.271 & 2.223\\
observations & 307,381 & 307,325 & 307,325 & 307,325 & 307,325 & 307,325\\
\midrule
controls & No & Yes & Yes & Yes & Yes & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
district & Yes & Yes & Yes & Yes & Yes & Yes\\
state-month & Yes & Yes & Yes & Yes & Yes & Yes\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. The outcome in each regression is days worked in the previous seven days. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:labor3month}Wind and labor allocation, by month}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & farm & non-farm\\
\midrule
May & -0.006 & -0.039\\
 & (0.068) & (0.070)\\
June & -0.136* & 0.114\\
 & (0.080) & (0.099)\\
July & -0.285** & 0.176\\
 & (0.142) & (0.134)\\
Aug. & 0.048 & -0.010\\
 & (0.086) & (0.069)\\
Sept. & 0.076 & -0.082\\
 & (0.085) & (0.091)\\
Oct. & 0.013 & -0.083\\
 & (0.076) & (0.059)\\
Nov. & -0.063 & -0.013\\
 & (0.062) & (0.075)\\
controls & Yes & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{}\\
district & Yes & Yes\\
year-month & Yes & Yes\\
\midrule
observations & 307,325 & 307,325\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in column one is .  * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

I perform a similar exercise with yield, the results of which are in Table \ref{tab:yield4monthly}. I include only the five months of the year that are used in the calculation of the yield estimates, or June through October. The results are again from two-stage least squares, with the F-statistics for each month presented at the bottom; monthly wind remains a strong predictor of pollution. Column one presents results without controls for weather while column two presents results with controls for weather; the differences in coefficients make clear how important the inclusion of weather is here.

@@

\caption{\label{tab:yield4monthly}Pollution and productivity, by month}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2)\\
\midrule
June & -0.325** & -0.736***\\
 & (0.135) & (0.062)\\
July & -0.778*** & 0.051\\
 & (0.151) & (0.095)\\
Aug. & -1.201*** & 0.087\\
 & (0.455) & (0.070)\\
Sept. & 1.270*** & -0.140\\
 & (0.427) & (0.180)\\
Oct. & -3.013*** & 0.334\\
 & (0.963) & (0.291)\\
weather & No & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{}\\
village & Yes & Yes\\
year & Yes & Yes\\
\midrule
F (June) & 1,063 & 972\\
F (July) & 2,090 & 2,200\\
F (Aug.) & 1,646 & 2,340\\
F (Sept.) & 2,025 & 2,024\\
F (Oct.) & 473 & 402\\
observations & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

A final caveat about these month-specific results is that they do not take into account possible interactions between different months. For example, yield might respond strongly to average pollution in June and July, which would not be captured in Table \ref{tab:yield4monthly}.

@@

\caption{\label{tab:yield7ivdiffindiff}Agricultural productivity and pollution source}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3)\\
\midrule
PM 2.5 & -0.299*** & -0.107* & -0.147**\\
 & (0.066) & (0.063) & (0.063)\\
PM 2.5 times coal & -0.328*** & -0.321*** & -0.304***\\
 & (0.026) & (0.024) & (0.023)\\
weather & No & Yes & Yes\\
weather (expanded) & No & No & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{}\\
year & Yes & Yes & Yes\\
village & Yes & Yes & Yes\\
\midrule
F (pm) & 766 & 776 & 788\\
F (pm times open) & 199 & 222 & 232\\
observations & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

@@

\caption{\label{tab:data}Data sources}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}>{\centering\arraybackslash}p{5cm}>{\centering\arraybackslash}p{3cm}>{\centering\arraybackslash}p{3cm}}
\toprule
  & source & geographic coverage & temporal coverage\\
\midrule
shapefile & Asher et al. (2021) & India & \\
coal plants & Global Energy Monitor & global & yearly\\
wind & NCAR & global & daily\\
pollution & Hammer et al. (2020) & global & monthly\\
agriculture & Gangopadhya et al. (2022) & India & two seasons/year\\
nightlights & Asher et al. (2021) & India & yearly\\
weather & TerraClimate & global & monthly\\
labor & National Sample Survey (NSS) & India & daily interviews\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Global Energy Monitor: globalenergymonitor.org/projects/global-coal-plant-tracker. NCAR: climatedataguide.ucar.edu/. TerraClimate: www.climatologylab.org/terraclimate.html
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\title{Blowing in the wind: Pollution and agricultural productivity in India\footnote{I thank Ariel Ortiz-Bobea, Marc Bellemare, and David Sungho Park for comments and suggestions that greatly improved the quality of the paper. The usual disclaimer applies. All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}}
\author{Joshua D. Merfeld\footnote{KDI School of Public Policy and Management and IZA; \href{mailto:merfeld@kdis.ac.kr}{\nolinkurl{merfeld@kdis.ac.kr}}}}
\date{2023-04-07}

@@

Sanders and Barreca (2022)

@@

\caption{\label{tab:plantresultstable}Local characteristics and the construction of coal plants}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{1991 census} & \multicolumn{2}{c}{2001 census} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
  & 1991 & 2001 & 2001 & 2011\\
\midrule
Population (log) & 0.010*** & 0.001*** & 0.017*** & 0.004***\\
 & (0.000) & (0.000) & (0.000) & (0.000)\\
Area (log) & -0.006*** & 0.001** & -0.015*** & -0.001***\\
 & (0.001) & (0.000) & (0.000) & (0.000)\\
Literacy (prop) & 0.024*** & 0.017*** & 0.032*** & 0.029***\\
 & (0.003) & (0.002) & (0.002) & (0.002)\\
Ag. productivity &  &  & 0.026*** & 0.004***\\
 &  &  & (0.001) & (0.000)\\
Sub-sample & all & no plant & all & no plant\\
\midrule
Observations & 283,021 & 264,265 & 508,784 & 469,004\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Robust standard errors are in parentheses. The outcome in the first column is whether the village is within 30km of a coal plant in 1991. The second column is whether a village in 1991 will have a coal plant in 2001, conditional on not having one in 1991. The last two columns are similarly defined, except using 2001 and 2011 as the years. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtable}Wind direction and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}}
\toprule
  & (1) & (2) & (3)\\
\midrule
Wind days & -0.0078*** & -0.0069*** & -0.0062***\\
 & (0.0007) & (0.0007) & (0.0006)\\
Rain (z) &  & 0.0854*** & -0.0424***\\
 &  & (0.0018) & (0.0046)\\
Mean temperature (10s) &  & -0.0021*** & 0.1321***\\
 &  & (0.0001) & (0.0034)\\
Rain squared &  &  & -0.0010***\\
 &  &  & (0.0001)\\
Temperature squared &  &  & -0.0002***\\
 &  &  & \vphantom{1} (0.0000)\\
Rain times Temperature &  &  & 0.0003***\\
 &  &  & (0.0000)\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{}\\
Village & Yes & Yes & Yes\\
Year & Yes & Yes & Yes\\
\midrule
Observations & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablepm}Particulate matter (PM 2.5) and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}}
\toprule
  & (1) & (2) & (3)\\
\midrule
Particulate matter & -0.042*** & -0.044*** & -0.032***\\
(log PM 2.5) & (0.003) & (0.003) & (0.003)\\
Weather & No & Yes & Yes\\
Weather (expanded) & No & No & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{}\\
Village & Yes & Yes & Yes\\
Year & Yes & Yes & Yes\\
\midrule
Observations & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtabletwo}Pollution and agricultural productivity, IV estimates}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3)\\
\midrule
Particulate matter & -0.941*** & -0.813*** & -0.728***\\
(log PM 2.5) & (0.078) & (0.076) & (0.075)\\
Weather & No & Yes & Yes\\
Weather (expanded) & No & No & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{}\\
Village & Yes & Yes & Yes\\
Year & Yes & Yes & Yes\\
\midrule
F (first stage) & 1,236 & 1,263 & 1,264\\
Observations & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

\hypertarget{robustness-checks}{%
\subsection{Robustness checks}\label{robustness-checks}}

\begin{figure}
\includegraphics{draft_files/figure-latex/randomplot-1} \caption[Randomization inference]{Randomization inference}\label{fig:randomplot}\floatfoot*{Note: The figure presents the distribution of coefficients by randomly assigning wind direction across villages within the same year. The "all" distribution is created by randomly assigning a single wind value to each village, sampled with replacement across all villages in a given year. The "within district" randomly samples with replacement only from within the same district in the same year.}
\end{figure}

\caption{\label{tab:yieldtableleads}Agricultural productivity and pollution leads}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2)\\
\midrule
Particulate matter & -1.152*** & -1.067***\\
(log PM 2.5) & (0.075) & (0.071)\\
Particulate matter & 0.068 & 0.268***\\
(one-year lead) & (0.072) & (0.074)\\
Weather & No & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{}\\
Village & Yes & Yes\\
Year & Yes & Yes\\
\midrule
F (current) & 974 & 1,036\\
F (lead) & 612 & 597\\
Observations & 1,161,265 & 1,161,265\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions estimated agricultural yield (tons per hectare). * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablehet}Heterogeneity in the effects of pollution on productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Wind} & \multicolumn{2}{c}{Yield} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
  & >p(50) & <=p(50) & >p(50) & <=p(50) & \\
\midrule
Particulate matter & -0.767*** & -0.328*** & -1.130*** & -0.690*** & -0.409**\\
(log PM 2.5) & (0.104) & (0.095) & (0.060) & (0.146) & (0.160)\\
PM times Rain &  &  &  &  & 0.061***\\
 &  &  &  &  & (0.014)\\
Weather & Yes & Yes & Yes & Yes & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
Village & Yes & Yes & Yes & Yes & Yes\\
Year & Yes & Yes & Yes & Yes & Yes\\
\midrule
F (1st stage, PM) & 684 & 491 & 688 & 484 & 865\\
F (1st stage, PM times rain) &  &  &  &  & 1,437\\
Observations & 617,804 & 649,118 & 634,342 & 632,580 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. The first two columns split the sample based on the median exposure (by village). The second two columns split the sample based on initial -- the first year available -- agricultural productivity. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:labortable}Wind direction and labor allocation by rural status}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}}
\toprule
  & All & All & Self & Wage & Farm & Non-farm\\
\midrule
\textbf{Panel A: all} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
Wind & -0.011 & -0.009 & 0.030 & -0.049 & -0.009 & -0.010\\
 & (0.031) & (0.034) & (0.039) & (0.034) & (0.034) & (0.033)\\
DV mean & 3.303 & 3.303 & 1.862 & 1.442 & 0.789 & 2.514\\
Observations & 523,075 & 522,957 & 522,957 & 522,957 & 522,957 & 522,957\\
\midrule
\textbf{Panel B: Rural} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
Wind & -0.006 & -0.034 & 0.068 & -0.102*** & -0.024 & -0.010\\
 & (0.044) & (0.040) & (0.043) & (0.035) & (0.043) & (0.036)\\
DV mean & 3.494 & 3.494 & 2.184 & 1.311 & 1.271 & 2.223\\
Observations & 307,381 & 307,325 & 307,325 & 307,325 & 307,325 & 307,325\\
\midrule
Controls & No & Yes & Yes & Yes & Yes & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
District & Yes & Yes & Yes & Yes & Yes & Yes\\
State-month & Yes & Yes & Yes & Yes & Yes & Yes\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. The outcome in each regression is days worked in the previous seven days. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:labor3month}Heterogeneity by month}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Labor} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-3}
  & Farm & Non-farm & Yield\\
\midrule
June & -0.128* & 0.123 & -0.736***\\
 & (0.076) & (0.095) & (0.062)\\
July & -0.278* & 0.185 & 0.051\\
 & (0.142) & (0.133) & (0.095)\\
Aug. & 0.055 & -0.002 & 0.087\\
 & (0.083) & (0.068) & (0.070)\\
Sept. & 0.086 & -0.072 & -0.140\\
 & (0.081) & (0.093) & (0.180)\\
Oct. & 0.022 & -0.074 & 0.334\\
 & (0.071) & (0.057) & (0.291)\\
controls & Yes & Yes & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{}\\
district & Yes & Yes & Yes\\
year-month & Yes & Yes & Yes\\
\midrule
observations & 307,325 & 307,325 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in column one is farm labor, the outcome is column two is non-farm labor, and the outcome in column three is village-level productivity. The independent variable for labor is wind, while the IV approach above is still used for yield. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

I perform a similar exercise with yield, the results of which are in Table \ref{tab:labor3month}. I include only the five months of the year that are used in the calculation of the yield estimates, or June through October. The results are again from two-stage least squares, with the F-statistics for each month presented at the bottom; monthly wind remains a strong predictor of pollution. Column one presents results without controls for weather while column two presents results with controls for weather; the differences in coefficients make clear how important the inclusion of weather is here.

@@

A final caveat about these month-specific results is that they do not take into account possible interactions between different months. For example, yield might respond strongly to average pollution in June and July, which would not be captured in Table \ref{tab:labor3month}.

@@

\caption{\label{tab:yield7ivdiffindiff}Agricultural productivity and pollution source}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3)\\
\midrule
Particulate matter & -0.299*** & -0.107* & -0.147**\\
(log PM 2.5) & (0.066) & (0.063) & (0.063)\\
PM 2.5 times Coal & -0.328*** & -0.321*** & -0.304***\\
 & (0.026) & (0.024) & (0.023)\\
Weather & No & Yes & Yes\\
Weather (expanded) & No & No & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{}\\
Year & Yes & Yes & Yes\\
Village & Yes & Yes & Yes\\
\midrule
F (PM) & 766 & 776 & 788\\
F (PM times Coal) & 199 & 222 & 232\\
Observations & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\leavevmode\vadjust pre{\hypertarget{ref-sanders2022adaptation}{}}%
Sanders, Nicholas J, and Alan I Barreca. 2022. {``{Adaptation to Environmental Change: Agriculture and the Unexpected Incidence of the Acid Rain Program}.''} \emph{{American Economic Journal: Economic Policy}} 14 (1): 373--401.

@@

\caption{\label{tab:data}Data sources}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}>{\centering\arraybackslash}p{5cm}>{\centering\arraybackslash}p{3cm}>{\centering\arraybackslash}p{3cm}}
\toprule
  & source & geographic coverage & temporal coverage\\
\midrule
shapefile & Asher et al. (2021) & India & \\
coal plants & Global Energy Monitor & global & yearly\\
wind & NCAR & global & daily\\
pollution & Hammer et al. (2020) & global & monthly\\
agriculture & Gangopadhya et al. (2022) & India & two seasons/year\\
weather & TerraClimate & global & monthly\\
labor & National Sample Survey (NSS) & India & daily interviews\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Global Energy Monitor: globalenergymonitor.org/projects/global-coal-plant-tracker. NCAR: climatedataguide.ucar.edu/. TerraClimate: www.climatologylab.org/terraclimate.html
\end{tablenotes}
\end{threeparttable}
\end{table}
